LSST Alerts: Science-Driven Options for Packets and their Distribution

### 2020-01-07 dmtn-tbd.tex
drafted S4

Pre-filtered streams might mean the alerts can be distributed to more brokers than numStreams. What kind of pre-filters might suit the brokers?

 - magnitude or signal-to-noise ratio (affects completeness/purity)
 - region of sky (like one of the LOI for a particular region)
 - static-sky object association

 Image free streams of alert packets.
 Sources only associated with past alerts.

Provide estimates for how much the alert stream volume would be reduced.

>>>>

This section explores the scientific motivation and impact of offering brokers pre-filtered alert streams. 
Pre-filtering could reduce the overall bandwidth of alert distribution and potentially allow streams to be transmitted to more brokers, thereby enabling more alerts-related science.
Providing pre-filtered streams could also lessen the load and resources used by the brokers, enabling more alerts-related science by allowing brokers to spend a smaller fraction of their budget computational resources.

The types of pre-filters that a broker would use are mainly driven by the science goals of that particular broker; some examples follow.
A broker might only find it useful to receive alerts for {\tt DIASources} that are likely to be stellar variables, moving objects, or extragalactic transients.
A broker might only want to receive alerts that could potentially be observed by its associated follow-up resources -- {\tt DIASources} brighter than a given limit or located in a particular region of sky. 
A broker might employ a suite of algorithms that all require, e.g., at least two detections by LSST before any further action is taken, and so would not need any single-detection alerts.
A broker might be specialized in a science area that is not done with the wide-fast-deep main survey, but with a special program such as the deep drilling fields or target-of-opportunity imaging surveys. 
Finally, a broker might not be interested in alerts obtained during poor weather conditions (e.g., an image quality or sky background violating some limit) -- although, this type of filter might not be entirely science-driven.

For the above reasons, the potential pre-filters that might be scientifically useful -- some of which have been suggested by brokers already -- include:
\begin{itemize}
\item {\bf Apparent Magnitude: } only {\tt DIASources} brighter than a specified apparent magnitude (for each of the LSST filters {\it ugrizy}) are transmitted. 
\item {\bf Region of Sky: } only {\tt DIASources} in a given sky area(s) are transmitted. 
\item \texttt{\bf DIAObject} {\bf History: } only {\tt DIASources} associated with {\tt DIAObjects} that have at least $N$ previous detections are transmitted, where $N$ can be $\geq1$. 
\item \texttt{\bf SSObject} {\bf Association: } only {\tt DIASources} that are associated with a {\tt SSObject} are transmitted. (Potentially including new, unassociated {\tt DIASources}, because they might also be moving objects).
\item \texttt{\bf Object} {\bf Association: } only {\tt DIASources} associated with {\tt DIAObjects} that are, in turn, associated with a data release {\tt Object} that meets some specification are transmitted (e.g., associated with a stellar point source).
\item {\bf Observation Metadata: } only alerts from images obtained with a given set of metadata, e.g., a special observing program or meeting sky condition thresholds, are transmitted.
\end{itemize}

All of these potential science-driven pre-filters are based on the information contained in the alert itself, and do not impose any additional processing on the Prompt pipeline.

\textcolor{red}{Provide estimates for how much the alert stream volume would be reduced by each of these potential pre-filters using nominal limits.}
